### 2011-08-08 doc/theses/vitasek/diplomka.tex
Thesis: adding schema of inference.

At heart of jInfer inference process is a modular system provided by NetBeans Platform allowing to define services (interfaces), implement them in any number of ways and then let the user choose which implementation to use. Most importantly, the whole process consists of 3 consecutive steps (see TODO link obrazok), responsibility of 3 different services - interchangeable modules.

>>>>

At heart of jInfer inference process is a modular system provided by NetBeans Platform allowing to define services (interfaces), implement them in any number of ways and then let the user choose which implementation to use. Most importantly, the whole process consists of 3 consecutive steps (see TODO link picture - inference process), responsibility of 3 different services - interchangeable modules.
